MCTS Applied to Co-operative Problems

### 2015-08-05 Report/response.tex

\paragraph*{\textit{"Doors are rendered in Black." -> "Walls are rendered in Black."}}
We have corrected the typo in the definition of \emph{Walls} in the problem domain section.
\subsection{Review 4 (Reviewer B)}
\paragraph*{\textit{there is some mixup with agents being labeled 0 and 1 in the figures, but 1 and 2 in the text.}}
That section has been removed due to another comment that we received and so the mixup is gone.

\paragraph*{\textit{I did not understand the terms "UCT border" and "rollout border". Explain them. Are they related to "Max UCT" and "Max Rollout" in Fig. 2 ?}}
Both have been reworded to a more used set of terminology.
\paragraph*{\textit{What does 1+1 ES mean?}}
The paper has been expanded to include a brief description of the 1+1 ES technique.
\paragraph*{\textit{I did not quite understand how your MCTS works with multiple agents. Are you running independent simulations for each agent (I assume yes but it was not clear)? }}
Yes, each agent was running independent simulations. It has been made clearer in the paper that none of the agents have the ability to communicate with another agent, and that each agent is controlled by a single controller. 
\paragraph*{\textit{I would like to see results for mixed agent teams.}}
\paragraph*{\textit{The issue of communication, especially learning communication, is very important and I suggest you focus on this for future research.}}
Have expanded the section in future work on communication to better reflect this.
\subsection{Review 5 (Reviewer F)}
\paragraph*{\textit{The early segments fail to really discuss the MCTS algorithm.  The abbreviation for this is also found in the abstract and should really be in the introductory paragraph.}}
The MCTS algorithm was given some background in the literature as to its previous applications and a summary of its typical behaviour. Have added a small section describing its creation and referenced the key papers for that.
Have removed the abbreviation for MCTS from the abstract.
\paragraph*{\textit{Section II covering preliminary tests is light on technical details and seem ill placed when you consider the subsequent studies later on in the paper.}}
We have removed this section to make way for more detailed results
\paragraph*{\textit{The third page could do with being structured better.  The charts are ill-placed, do not help the flow of the authors argument and need better captions.}}
\paragraph*{\textit{The paper would benefit from showing the actual levels used as part of the testing.  Given it makes it harder to understand the impact of later levels.  Figure 10 should be shown much earlier in the paper.}}
\paragraph*{\textit{The selection of controller types does strike me as odd.  With a random selected and a Variable MAGA that is introduced to resolve shortcoming of the other.  What about a simple 1+1 ES without the macro's?  Or the likes of an A* bot?  Could these not be implemented?}}
A simple 1+1 ES would not be able to find a good solution within the time limits of real time video games. Macro Actions has been proven to vastly improve the ability of GA's to solve complex real time problems such as in Perez et al \cite{perez2013rolling}. A* was considered to have too high a branching factor in this problem but was decided to be investigated in future work.
\paragraph*{\textit{More than once the idea of a language through which to communicate is discussed, but it has no real impact on this paper and should really be saved for when it is explored}}

### 2015-08-05 Report/response.tex

\documentclass{article}
\title{Response}

\begin{document}
\maketitle
\section{Response to the reviewers}
We have placed the reviewers comments in \textit{\textbf{Italics and Bold}} and our response to those comments in plain text.

\subsection{Review 1 (Reviewer A)}
\paragraph*{\textit{Introduction: The introduction is well written but oddly doesn't contain discussion about cooperative games. The introduction starts by discussing general game playing (which is not a main topic of the paper) and then presents MCTS (which is) but the discussion of cooperative games is missing.}}
Added section on co-operative games.

@@

\paragraph*{\textit{"Doors are rendered in Black." -> "Walls are rendered in Black."}}
We have corrected the typo in the definition of \emph{Walls} in the problem domain section.
\subsection{Review 4 (Reviewer B)}
\paragraph*{\textit{there is some mixup with agents being labeled 0 and 1 in the figures, but 1 and 2 in the text.}}
That section has been removed due to another comment that we received and so the mixup is gone.

\paragraph*{\textit{I did not understand the terms "UCT border" and "rollout border". Explain them. Are they related to "Max UCT" and "Max Rollout" in Fig. 2 ?}}
Both have been reworded to a more used set of terminology.
\paragraph*{\textit{What does 1+1 ES mean?}}
The paper has been expanded to include a brief description of the 1+1 ES technique.
\paragraph*{\textit{I did not quite understand how your MCTS works with multiple agents. Are you running independent simulations for each agent (I assume yes but it was not clear)? }}
Yes, each agent was running independent simulations. It has been made clearer in the paper that none of the agents have the ability to communicate with another agent, and that each agent is controlled by a single controller. 
\paragraph*{\textit{I would like to see results for mixed agent teams.}}
Figures 6 and 7 have been retitled to better show that they were results for mixed agent teams.
\paragraph*{\textit{The issue of communication, especially learning communication, is very important and I suggest you focus on this for future research.}}
Have expanded the section in future work on communication to better reflect this.
\subsection{Review 5 (Reviewer F)}
\paragraph*{\textit{The early segments fail to really discuss the MCTS algorithm.  The abbreviation for this is also found in the abstract and should really be in the introductory paragraph.}}
The MCTS algorithm was given some background in the literature as to its previous applications and a summary of its typical behaviour. Have added a small section describing its creation and referenced the key papers for that.
Have removed the abbreviation for MCTS from the abstract.
\paragraph*{\textit{Section II covering preliminary tests is light on technical details and seem ill placed when you consider the subsequent studies later on in the paper.}}
We have removed this section to make way for more detailed results
\paragraph*{\textit{The third page could do with being structured better.  The charts are ill-placed, do not help the flow of the authors argument and need better captions.}}
\paragraph*{\textit{The paper would benefit from showing the actual levels used as part of the testing.  Given it makes it harder to understand the impact of later levels.  Figure 10 should be shown much earlier in the paper.}}
\paragraph*{\textit{The selection of controller types does strike me as odd.  With a random selected and a Variable MAGA that is introduced to resolve shortcoming of the other.  What about a simple 1+1 ES without the macro's?  Or the likes of an A* bot?  Could these not be implemented?}}
A simple 1+1 ES would not be able to find a good solution within the time limits of real time video games. Macro Actions has been proven to vastly improve the ability of GA's to solve complex real time problems such as in Perez et al \cite{perez2013rolling}. A* was considered to have too high a branching factor in this problem but was decided to be investigated in future work.
\paragraph*{\textit{More than once the idea of a language through which to communicate is discussed, but it has no real impact on this paper and should really be saved for when it is explored}}

### 2015-08-05 Report/ceec.tex
Worked on the introduction with co-operative games

\newacronym{mcts}{MCTS}{Monte-Carlo Tree Search}
\newacronym{uct}{UCT}{Upper Confidence bound applied to Trees}
\newacronym{ggp}{GGP}{General Game Playing}
\newacronym{ga}{GA}{Genetic Algorithm}
\newacronym{mas}{MAS}{Multi-Agent Systems}
\newacronym{maga}{MAGA}{Macro Action Genetic Algorithm}
\newacronym{ai}{AI}{Artificial Intelligence}

@@

>>>>

\newacronym{mcts}{MCTS}{Monte-Carlo Tree Search}
\newacronym{uct}{UCT}{Upper Confidence bound applied to Trees}
\newacronym{ggp}{GGP}{General Game Playing}
\newacronym{ga}{GA}{Genetic Algorithm}
\newacronym{mas}{MAS}{Multi-Agent Systems}
\newacronym{maga}{MAGA}{Macro Action Genetic Algorithm}
\newacronym{ai}{AI}{Artificial Intelligence}
\newacronym{fps}{FPS}{First-Person Shooter}
\newacronym{rts}{RTS}{Real-Time Strategy}
\newacronym{rpg}{RPG}{Role-Playing Game}

@@

Games that feature co-operation of some form between human players and \gls{ai} agents are commonplace. Most however feature very limited forms of co-operation that are typically scripted such as in most \gls{fps} games. Typically \gls{fps} games give the mere impression of co-operation, though any player that looks carefully at it will see the tell tale signs of scripting. Where \gls{fps} games typically excel at co-operation is in online modes that enable teams of humans to play against each other. Some games even provide squad structures and communication allowing direct command for the purpose of better co-ordination as in Battlefield 2142 \cite{battlefield2142}. \gls{rts} games also often have a small number of features designed to facilitate communication in a bid to facilitate co-operation. Two games that stand out for co-operation are Microsoft's Rise of Nations \cite{riseofnations} and Mad Doc Software's Empire Earth 2 \cite{empireEarth2}. Rise of Nations allowed a human and \gls{ai} player to operate the same set of units and buildings, though no communication was possible at all. This allowed a form of co-operation but the \gls{ai} operated to its own agenda. Empire Earth 2 allowed for humans and \gls{ai} agents to co-operate by letting plans be drawn up between them that could also be followed by both the human and \gls{ai} agent. These allowed a fairly complex set of instructions to be created, despite the simple interface.

A highly popular game that had an entire mode designed for co-operation between humans was Valve's Portal 2 \cite{portal2}. This featured human sized lab test mazes with elements that required players to work together by activating buttons, moving cubes and using intra-dimensional portals to get to the end goal. Both players were required to reach the goal in order to complete the level.
